Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Young Validated Planet in IC~2602

### 2020-07-22 paper/ms.tex
Update manuscript
Co-authored-by: Andrew Mann <awmann@unc.edu>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
  Members (black circles) were identified by
  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
  within 5 standard deviations of the mean \cn\ right ascension,
  declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
  $Bp$ Gaia blue, and $Rp$ Gaia red.  MIST isochrones (colored lines)
  fit the upper main sequence well, but diverge from the data for
  $M_\star \lesssim 0.7 M_\odot$. This is a known problem with PMS
  models (see Section~\ref{subsec:hr}).
  \label{fig:hr}
	}
\end{figure}

@@

Figure~\ref{fig:hr} also compares the data to the MIST isochrones
\citep{choi_mesa_2016}.  We used the
web-interace\footnote{\url{http://waps.cfa.harvard.edu/MIST/interp_isos.html},
\texttt{2020-07-08}} to interpolate isochrones at 10, 20, 30, and 40
million years. We assumed solar metallicity, and a fixed extinction
value of $A_V = 0.217$ \citep{randich_gaiaeso_2018}.  The 30 and 40
Myr models align well with the data for stars with masses ranging from
roughly $0.7$--$7\,M_\odot$.  The PMS K and M dwarf models are bluer
than observed in the Gaia photometry.  This discrepancy was noted and
discussed at length by \citet{choi_mesa_2016}.  One suggested
explanation was that strong magnetic fields in low-mass
pre-main-sequence stars inhibit convection and produce a high filling
factor of starspots \citep[{\it
e.g.},][]{stauffer_why_2003,feiden_magnetic_2013}.  This explanation
however fails to explain poor isochrone fits in old open clusters
({\it e.g.}, M$\,$67) as well as the field, particularly in blue
bandpasses. A more likely explanation could be that the molecular line
lists for M dwarf atmospheres are incomplete in these wavelength
ranges.

@@

%\clearpage
\acknowledgements
%\raggedbottom

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
  Members (black circles) were identified by
  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
  within 5 standard deviations of the mean \cn\ right ascension,
  declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
  $Bp$ Gaia blue, and $Rp$ Gaia red.  MIST isochrones (colored lines)
  fit the upper main sequence well, but diverge from the data for
  $M_\star \lesssim 0.7 M_\odot$. This is a known issue with the
  M dwarf models (see Section~\ref{subsec:hr}).
  \label{fig:hr}
	}
\end{figure}

@@

Figure~\ref{fig:hr} also compares the data to the MIST isochrones
\citep{choi_mesa_2016}.  We used the
web-interace\footnote{\url{http://waps.cfa.harvard.edu/MIST/interp_isos.html},
\texttt{2020-07-08}} to interpolate isochrones at 10, 20, 30, and 40
million years. We assumed solar metallicity, and a fixed extinction
value of $A_V = 0.217$ \citep{randich_gaiaeso_2018}.  The 30 and 40
Myr models align well with the data for stars with masses ranging from
roughly $0.7$--$7\,M_\odot$.  The PMS K and M dwarf models are bluer
than observed in the Gaia photometry.  This discrepancy was noted and
discussed at length by \citet{choi_mesa_2016}.  One suggested
explanation was that strong magnetic fields in low-mass
pre-main-sequence stars inhibit convection and produce a high filling
factor of starspots \citep[{\it
e.g.},][]{stauffer_why_2003,feiden_magnetic_2013}.  This explanation
however fails to explain poor isochrone fits in both old open clusters
({\it e.g.}, M$\,$67) and the field, particularly in blue bandpasses.
An alternative explanation is that the molecular line lists for M
dwarf atmospheres are incomplete in these wavelength ranges
\citep{rajpurohit_effective_2013,mann_spectrothermometry_2013}.

@@

%\clearpage
\acknowledgements
\raggedbottom
